We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-03 paper/paper.tex
some pagragraphs

To

It has been shown that LG pair separation vector is aligned along the
filaments in  which they are typically embeded
\cite{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
matter arrangements are aligned with the plane itself. 
Characterizing the satellite alignments with $\mu$ thus provide
information about how satellites are distributed with respect to the
cosmic web.

@@

From this tensor we compute its eigenvalues,
$\lambda_1>\lambda_2>\lambda_3$, and corresponding eigenvectors,
$\hat{I}_1$, $\hat{I}_2$, $\hat{I}_3$.
We define the size of the three ellipsoidal axis as
$a=\sqrt{\lambda_1}$, $b=\sqrt{\lambda_2}$ and $c=\sqrt{\lambda_3}$.
We also define $\hat{n}\equiv \hat{I}_1$ as the vector perpendicular to the
planar satellite distribution. 
We also define the width, $w$, of the planar satellite distribution,
$\sigma_p$ as the standard deviation of all satellite distances to the
plane defined by the vector $\hat{n}$. 
Finally, we characterize the alignment between the satellite plane and the
vector connecting the two dominant galaxies by $\mu=|\hat{r}_{AB}\cdot
\hat{n}|$.

>>>>

Studies of the Local Group in an explicit cosmological context have
also renewed the interest on performing constrained simulations that
could reproduce the observed large scale structure of the Universe,
This has also motivated the study of the two dominant galaxies in the 
Local Group as a pair in a cosmological context.

@@

From this tensor we compute its eigenvalues,
$\lambda_1>\lambda_2>\lambda_3$, and corresponding eigenvectors,
$\hat{I}_1$, $\hat{I}_2$, $\hat{I}_3$.
We define the size of the three ellipsoidal axis as
$a=\sqrt{\lambda_1}$, $b=\sqrt{\lambda_2}$ and $c=\sqrt{\lambda_3}$.
We also define $\hat{n}\equiv \hat{I}_1$ as the vector perpendicular to the
planar satellite distribution. 
We also define the width, $w$, of the planar satellite distribution,
$\sigma_p$ as the standard deviation of all satellite distances to the
plane defined by the vector $\hat{n}$.

It has been shown that LG pair separation vector is aligned along the
filaments in  which they are typically embeded
\citep{2015ApJ...799...45F}, the LG pairs found in pancake-like DM
matter arrangements are aligned with the plane itself. 
Characterizing the satellite alignments with $\mu$ thus provide
information about how satellites are distributed with respect to the
cosmic web. 
For that reason we also characterize the alignment between the satellite plane and the
vector connecting the two dominant galaxies by $\mu=|\hat{r}_{AB}\cdot
\hat{n}|$.
